On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-22 MS.tex
Add section for table in Appendix Reorder Fig Appendix to match the ms Add section in Appendix with direction to "read.bib" file in github

\footnote{The correlation with RGR$_{\rm mass}$ is negative but becomes positive with AGR$_{\rm mass}$. For SLA, WD, Hmax, and Aarea, the direction of the predicted relationship is not affected by the growth measurement used. However RGR and AGR are fundamentally different for a lot of ecologists. So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.}
\footnote{We have different expectation for SLA in AGRmass for seedling: but none of our data are in AGRmass, they are mainly in RGRmass (Fig. \ref{fig:figA8}). Why a change with WD when it is measured in mass? All WD seedling are measured in RGRmass, and there are some mass data for both other stages too. }

@@

Plants with high SLA can deploy a unit of leaf area more cheaply. However, high-SLA species also have shorter leaf lifespan, and must use more energy replacing leaves lost via turnover \citep{Wright:2004jb}. These two effects occur within the terms  $\frac{\ud B}{\ud t}$ and $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ in the above model. Whether plant growth rate increases with SLA depends on how the relative magnitude of the benefit (cheap leaf construction, via $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ ) and cost (higher leaf turnover, via $\frac{\ud B}{\ud t}$) of increased SLA change with size (Table \ref{tab:trade-offs}). 
During early life, when leaf comprises a large part of the plant, decreasing SLA has an overwhelmingly positive effect on height and diameter growth rate, because the effect of reducing $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ has a large effect compared to the other terms in eq. \ref{eq:daldmt}. For mass growth, cheaper leaf construction (high SLA) translates directly into faster relative growth rate in seedlings (See Appendix XXX eq. \ref{eq:eq1_seedlings_RGR}). As plants increase in size, however, the cost of building sapwood ($\frac{\ud M_{\rm s}}{\ud A_{\rm l}}$) increases disproportionately, decreasing the benefit of cheaper leaf construction in eq.  \ref{eq:daldmt}. Consequently, the relative effect of leaf turnover comes to dominate at larger sizes, and as such, the effect of SLA on height and diameter growth shifts from positive to negative as plants increase in size.

@@

As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do,Thomas-2011, Wenk:2015jz}). This effect occurs in the term $\frac{\ud M_{\rm t}}{\ud B}$ in the above model eqs. (\ref{eq:eq2}-\ref{eq:eq5}). For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth (i.e. $\frac{\ud M_{\rm t}}{\ud B} =1$). But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth. Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates (Table \ref{tab:trade-offs}).

@@

In total we inspected the full text of 583 articles (see Appendix XXXX in Supplementary material for list). Individual studies had to report the following information to be included in our dataset: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size or stage of plants. Despite searching only on SLA and WD, we recorded coefficient correlations for a list of 19 traits in total: the five for which we had prior expectations, plus any of 14 others commonly used in the trait literature. Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or AGR measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g. fertilization, shade, salt stress). In some cases, we asked the authors for additional information about the specific correlation coefficient value when this was not already provided.

@@

% x <- remake::make("CleanData")
% unqiue(x$ref)
% nrow(x)
% x <- remake::make("CompleteData")
% unique(x$ref)
% nrow(x)
% x <- remake::make("IdealData")
% unique(x$ref)
% nrow(x)

@@

For SLA, the correlation between RGR and the trait changed significantly with plant size in the manner expected (Fig. \ref{fig:fig3}a). The correlation between RGR and SLA shifted from strongly positive at seedling stage ($\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero). The correlation coefficients recorded at sapling stage were intermediate between seedling and adult stages. Model fit improved significantly when stage was incorporated (see log likelihood ratio tests, Fig. \ref{fig:fig3}a; average values for the coefficients ($\bar{r}$) in Fig. \ref{fig:figA4}a-e).

@@

Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}). The impact of publication bias was seemingly trivial (Appendix E, Fig. \ref{fig:figA7}). The extent of heterogeneity was high, but was substantially explained by our core hypothesis of a plant stage effect for SLA and seed mass (Appendix E). There was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig. \ref{fig:figA9}). Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. \ref{fig:figA5}).

\subsection*{Representation of stages among 19 traits}
In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig. \ref{fig:fig1}). We had thought it likely that for some traits correlations would be reported only for one size class. But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages. However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single stage (Fig. \ref{fig:fig1}).

@@

\clearpage
\begin{table}[h!]
\centering
\caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed?\\
  \hline
  1.& Reporting full details of bibliographic searches & yes	& Complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
  2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''. A full list of all articles evaluated is available in the Appendix \ref{app:literature-snapshot}.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	``Material and Methods'' for details.\\
 4.& Specifying meta-analytical model &	yes	& We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect. See ``Material and Methods'' for details. Results are shown in Fig. \ref{fig:fig3} \& \ref{fig:fig4}.\\
 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
 6.& Exploring causes of heterogeneity & yes &	We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
 7.& Multifactorial analysis of explanatory variable	& yes & We check whether several other explanatory moderators (i.e. growth measurement, experiment type or growth form) are consistently the strongest predictors of the data. We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See in Figs \ref{fig:figA6}.\\
  8.& Testing for publication bias &	yes	& We used several methods (i.e. funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number). See Appendix \ref{app:supp_info_analyses} for details.\\
  9.& Sensitivity analysis &	yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig4} \& \ref{fig:figA5}.\\
  10.& Exploring temporal changes in effect size &	yes	& See Appendix \ref{app:supp_info_analyses} for details.\\
  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used &	yes	& See sections in ``Material and Methods'' and ``Availability of code and data''.\\
 13.& Providing reference list of primary studies included in the analysis &	yes &	All articles from which data were extracted are cited in the paper.\\
  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the data set is available. See ``Availability of code and data'' for details.\\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}

@@

\clearpage
\section{Supporting Analyses}\label{app:supp_info_analyses}

@@

@@

\subsection{Simplified growth equations for seedlings of similar size}

\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}

>>>>

\footnote{The correlation with RGR$_{\rm mass}$ is negative but becomes positive with AGR$_{\rm mass}$. For SLA, WD, Hmax, and Aarea, the direction of the predicted relationship is not affected by the growth measurement used. However RGR and AGR are fundamentally different for a lot of ecologists. So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR. => We have different expectation for SLA in AGRmass for seedling: but none of our data are in AGRmass, they are mainly in RGRmass (Fig. \ref{fig:figA8}). Why a change with WD when it is measured in mass? All WD seedling are measured in RGRmass, and there are some mass data for both other stages too. }

@@

Plants with high SLA can deploy a unit of leaf area more cheaply. However, high-SLA species also have shorter leaf lifespan, and must use more energy replacing leaves lost via turnover \citep{Wright:2004jb}. These two effects occur within the terms  $\frac{\ud B}{\ud t}$ and $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ in the above model. Whether plant growth rate increases with SLA depends on how the relative magnitude of the benefit (cheap leaf construction, via $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ ) and cost (higher leaf turnover, via $\frac{\ud B}{\ud t}$) of increased SLA change with size (Table \ref{tab:trade-offs}). 
During early life, when leaf comprises a large part of the plant, decreasing SLA has an overwhelmingly positive effect on height and diameter growth rate, because the effect of reducing $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ has a large effect compared to the other terms in eq. \ref{eq:daldmt}. For mass growth, cheaper leaf construction (high SLA) translates directly into faster relative growth rate in seedlings (See Appendix \ref{app:growth-equation} eq. \ref{eq:eq1_seedlings_RGR}). As plants increase in size, however, the cost of building sapwood ($\frac{\ud M_{\rm s}}{\ud A_{\rm l}}$) increases disproportionately, decreasing the benefit of cheaper leaf construction in eq.  \ref{eq:daldmt}. Consequently, the relative effect of leaf turnover comes to dominate at larger sizes, and as such, the effect of SLA on height and diameter growth shifts from positive to negative as plants increase in size.

@@

As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do,Thomas-2011, Wenk:2015jz}). This effect occurs in the term $\frac{\ud M_{\rm t}}{\ud B}$ in the above model eqs. (\ref{eq:eq2}-\ref{eq:eq4}). For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth (i.e. $\frac{\ud M_{\rm t}}{\ud B} =1$). But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth. Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates (Table \ref{tab:trade-offs}).

@@

In total we inspected the full text of 583 articles (see Appendix \ref{app:literature-list} for list). Individual studies had to report the following information to be included in our dataset: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size or stage of plants. Despite searching only on SLA and WD, we recorded coefficient correlations for a list of 19 traits in total: the five for which we had prior expectations, plus any of 14 others commonly used in the trait literature. Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or AGR measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g. fertilization, shade, salt stress). In some cases, we asked the authors for additional information about the specific correlation coefficient value when this was not already provided.

@@

% x <- remake::make("CleanData")
% unqiue(x$ref)
% nrow(x)
% x <- remake::make("CompleteData")
% unique(x$ref)
% nrow(x)
% x <- remake::make("IdealData")
% unique(x$ref)
% nrow(x)
\subsection*{Representation of stages among 19 traits}
In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig. \ref{fig:fig1}). We had thought it likely that for some traits correlations would be reported only for one size class. But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages. However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single stage (Fig. \ref{fig:fig1}).

@@

For SLA, the correlation between RGR and the trait changed significantly with plant size in the manner expected (Fig. \ref{fig:fig3}a). The correlation between RGR and SLA shifted from strongly positive at seedling stage ($\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero). The correlation coefficients recorded at sapling stage were intermediate between seedling and adult stages. Model fit improved significantly when stage was incorporated (see log likelihood ratio tests, Fig. \ref{fig:fig3}a; average values for the coefficients ($\bar{r}$) in Fig. \ref{fig:figA4}).

@@

Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}). The impact of publication bias was seemingly trivial (See Appendix \ref{app:growth-equation}, Fig. \ref{fig:figA7}). The extent of heterogeneity was high, but was substantially explained by our core hypothesis of a plant stage effect for SLA and seed mass (Appendix \ref{app:supp_info_analyses}). There was no indication of a temporal change in the effect size being reported within stages (Appendix \ref{app:supp_info_analyses}, Fig. \ref{fig:figA9}). Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. \ref{fig:figA5}).

@@

\clearpage
\begin{table}[h!]
\centering
\caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed?\\
  \hline
  1.& Reporting full details of bibliographic searches & yes	& Complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
  2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''. A full list of all articles evaluated is available in the Appendix \ref{app:literature-list}.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	``Material and Methods'' for details.\\
 4.& Specifying meta-analytical model &	yes	& We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect. See ``Material and Methods'' for details. Results are shown in Fig. \ref{fig:fig3} \& \ref{fig:fig4}.\\
 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
 6.& Exploring causes of heterogeneity & yes &	We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
 7.& Multifactorial analysis of explanatory variable	& yes & We check whether several other explanatory moderators (i.e. growth measurement, experiment type or growth form) are consistently the strongest predictors of the data. We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See in Figs \ref{fig:figA6}.\\
  8.& Testing for publication bias &	yes	& We used several methods (i.e. funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number). See Appendix \ref{app:supp_info_analyses} for details.\\
  9.& Sensitivity analysis &	yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig4} \& \ref{fig:figA5}.\\
  10.& Exploring temporal changes in effect size &	yes	& See Appendix \ref{app:supp_info_analyses} for details.\\
  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used &	yes	& See sections in ``Material and Methods'' and ``Availability of code and data''.\\
 13.& Providing reference list of primary studies included in the analysis &	yes &	All articles from which data were extracted are cited in the paper.\\
  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the data set is available. See ``Availability of code and data'' for details.\\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}

@@

\section{Supporting Tables}\label{app:supp_info_table}

\linespread{1}

\begin{table}[h!]
\centering
\caption{List of the nineteen traits targeted. Abbreviation,
definition and search term used in the meta-analysis}
\label{tab:lit_search}
\vspace{0.5cm}
{\footnotesize
\begin{tabular}{p{3cm}p{3cm}p{8cm}}
  \hline
Trait & Definition & Search terms \\
  \hline
Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
  LAR & Leaf area ratio & ``leaf area ratio'' \\
  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
   \hline
\end{tabular}
}
\end{table}

\section{Supporting Analyses}\label{app:supp_info_analyses}

\subsection{Simplified growth equations for seedlings of similar size}\label{app:growth-equation}

@@

\subsection{Full list of all articles evaluated}\label{app:literature-list}

In total we inspected the full text of 583 articles. The full list of these artciles is in the "read.bib" file available at
\smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.

@@

\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}\label{app:heterogeneity}

### 2016-01-22 ms_snapshotinfo.Rnw
Small editing in abstract Add comments in footnotes for theoritical expectation Small rewriting of results (add results for SLA RGR vs AGR in mass) Rewriting of "measurements under 'ideal' conditions Move paragraph about stage representativity among traits as a new subsection in results
Add section for table in Appendix Reorder Fig Appendix to match the ms Add section in Appendix with direction to "read.bib" file in github

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits. These results allow us to narrow our search considerably.

\linespread{1}

\begin{table}[h!]
\centering
\caption{List of the nineteen traits targeted. Abbreviation,
definition and search term used in the meta-analysis}
\label{tab:lit_search}
\vspace{0.5cm}
{\footnotesize
\begin{tabular}{p{3cm}p{3cm}p{8cm}}
  \hline
Trait & Definition & Search terms \\
  \hline
Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
  LAR & Leaf area ratio & ``leaf area ratio'' \\
  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
   \hline
\end{tabular}
}
\end{table}

>>>>

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits. Thus we narrow our search to only cover these two main traits.

### 2016-01-22 ms_snapshotinfo.tex
Small editing in abstract Add comments in footnotes for theoritical expectation Small rewriting of results (add results for SLA RGR vs AGR in mass) Rewriting of "measurements under 'ideal' conditions Move paragraph about stage representativity among traits as a new subsection in results
Add section for table in Appendix Reorder Fig Appendix to match the ms Add section in Appendix with direction to "read.bib" file in github

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was 70\% of the literature that would be captured by SLA and WD for the total 19 traits. These results allow us to narrow our search considerably.

\linespread{1}

\begin{table}[h!]
\centering
\caption{List of the nineteen traits targeted. Abbreviation,
definition and search term used in the meta-analysis}
\label{tab:lit_search}
\vspace{0.5cm}
{\footnotesize
\begin{tabular}{p{3cm}p{3cm}p{8cm}}
  \hline
Trait & Definition & Search terms \\
  \hline
Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
  LAR & Leaf area ratio & ``leaf area ratio'' \\
  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
   \hline
\end{tabular}
}
\end{table}

>>>>

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was 70\% of the literature that would be captured by SLA and WD for the total 19 traits. Thus we narrow our search to only cover these two main traits.
